Particle Interception as a Function of Reynolds Number and Collector Density

### 2020-10-11 code/analysis.Rmd
integrated sep 4 run into analysis.rmd

pumpfinal <- pump %>%
  filter(growth_days==0, date != 190417, date != 190802, # leaving out old control 
         dowel_density != "0232")

@@

>>>>

pumpfinal <- pump %>%
  filter(growth_days==0, !date %in% c(190417, 190802, 190926), # leaving out old control and 
         dowel_density != "0232")

@@

pumpfinal <- pumpfinal %>%
  mutate(date = as.factor(date))
